Tail Flexibility in the Degrees of Preferential

### 2025-05-08 paper.qmd
Add temporary section of comments w/ some minor edits in qmd

---
title: Tail Flexibility in the Degrees of Preferential
 Attachment Networks
format:
  nature-pdf:
    fig-pos: 'H'
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-basic
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: natbib
    keep-tex: true
    equal-margins: false
    number-sections: true
author:
  - name: Thomas William Boughen
    affiliations:
      - name: Newcastle University
        id: 1
        department: School of Mathematics, Statistics and Physics
  - name: Clement Lee
    affiliations:
      - ref: 1
  - name: Vianey Palacios Ramirez
    affiliations:
      - ref: 1
abstract: |
  Devising the underlying generating mechanism of a real-life network is difficult as, more often than not, only its snapshots are available, but not its full evolution. One candidate for the generating mechanism is preferential attachment which, in its simplest form, results in a degree distribution that follows the power law. Consequently, the growth of real-life networks that roughly display such power-law behaviour is commonly modelled by preferential attachment. However, the validity of the power law has been challenged by the presence of alternatives with comparable performance, as well as the recent findings that the right tail of the degree distribution is often lighter than implied by the body, whilst still being heavy. In this paper, we study a modified version of the model with a flexible preference function that allows super/sub-linear behaviour whilst also guaranteeing that the limiting degree distribution has a heavy tail. We relate the distributions tail heaviness directly to the model parameters, allowing direct inference of the parameters from the degree distribution alone.
keywords: [networks, discrete extremes, degree distribution]
bibliography: refs.bib

@@

@@

If the power law is an adequate model to use for real degree distributions has become a heated debate, with alternatives such as @Broido_2019 seeming to outperform the power law in some cases. Additionally, @lef24 find that for many real degree distributions the body may follow a power law, the right tail does not or at least seems to be lighter than is implied by the body whilst still being heavy. One method for modelling the tail of the degree distributions of real networks is to use a discretised variation of the generalised Pareto distribution (GPD) usually dubbed the Integer GPD (GPD) where $X|X>v \sim \mathrm{IGPD}(\xi,\sigma,v)$ is defined by the survival:

@@

[CL: Is the precise form of the IGPD needed here? The big picture is probably more important: extreme value methods have not been used in analysing degree distributions until recently, such as @vvvk19 and @lef24. Not using these methods essentially downweights the deviation of the vertices with large degrees, which have far more influence on the network than those with small degrees, from the power law behaviour.]

@@

Estimating the preference function used by network generative models like this is of great interest, with the potential to provide a deeper understanding of the relationships between the vertices in the network. Several papers and at least one R package (`PAfit`) have been dedicated to estimating the preference function that may have been used when a network was growing; one thing all these have in common is requiring access to a networks evolution data, something that is not always readily available or feasible to access. A method for estimating a preference function without this data available would be extremely useful.

[@rudas07] introduces theoretical results for this model with a general preference function in the cases that the network being generated is a tree ($m=1$); presenting an opportunity to design a preference function that will capture the behaviours observed in the degree distributions of real networks. Since they provide theoretical results for the limiting degree distribution, a model of this form would be able to be fitted to the degree distributions of real networks where the full evolution is not available, only a snapshot.

The rest of this paper is as follows: @sec-gpa looks at the theoretical limiting behaviour of a GPA model when $m=1$ according to the results from [@rudas07], going on to introduce a flexible class of preference functions that can guarantee a heavy tailed degree distribution while still being flexible in the body. @sec-rec shows that the preference function parameters can be fairly well recovered from the degree distributions of networks simulated from the GPA model using various functions of the class introduced in @sec-gpa. Having shown that for simulated data the model parameters are recoverable from the degree distribution alone, @sec-real builds upon this and attempts to fit the model to degree distributions of real networks; modelling not only the degree distribution itself but also the estimates for the parameters of the preference function assuming the networks evolved according to the GPA scheme. Ultimately, @sec-conc discusses the main results of the paper, pitfalls of this method and future work.

# General Preferential Attachment {#sec-gpa}

The focus of this section is the limiting degree distribution of a preferential attachment network with preference function $b(\cdot)$ where each vertex brings with it $m$ edges. This preference function is subject to the following conditions:

@@

Given these two conditions an expression for the survival of the limiting degree distribution can be found in the case that $m=1$; obtained by considering a branching process that is equivalent to the growth of the network, as in [@rudas07]. Theorem 1 from [@rudas07] states that for the tree $\Upsilon(t)$ at time $t$:

$$
\lim_{t\rightarrow\infty}\frac{1}{|\Upsilon(t)|}\sum_{x\in\Upsilon(t)}\varphi(\Upsilon(t)_{\downarrow x}) = \lambda^* \int_0^\infty e^{-\lambda^* t}\mathbb E\left[\varphi(\Upsilon(t))\right]dt
$$
where $\lambda^*$ satisfies $\hat\rho(\lambda^*)=1$.

@@

$$
\bar F(k) = \frac{\int_0^\infty e^{-\lambda^* t}\mathbb E\left[\mathbb I\left\{\text{deg}(x,\Upsilon(t))>k\right\}\right]dt}{\int_0^\infty e^{-\lambda^* t}dt} = \prod_{i=0}^k\frac{b(i)}{\lambda^* + b(i)}
$$
Additionally, using the fact that $f(k) = \bar F(k-1) - \bar F(k)$ the probability mass function (p.m.f.) can be shown to be:

$$
f(k) = \frac{\lambda^*}{\lambda^* + b(k)}\prod_{i=0}^{k-1}\frac{b(i)}{\lambda^*+b(i)},\qquad k\in\mathbb N.
$$

@@

$$
\lim_{k\rightarrow\infty}\Omega(F,n) = \lim_{k\rightarrow\infty}\frac{b(k+1)-b(k)}{\lambda^*}.
$$
:::

@@

Previously, in @krapivsky01, a preference function of the form $k^\alpha +\varepsilon$ has been considered. However, it has been noted that super-linear preferential attachment ($\alpha > 1$) leads to a degenerate limiting degree distribution where at some point one vertex gains the connection from every vertex that joins the network, additionally sub-linear preferential attachment ($\alpha <1$) has been shown to lead to a light tailed limiting degree distribution. Consider a preference function of the form:

$$
b(k) = \begin{cases}
k^\alpha + \varepsilon,&k<k_0\\
k_0^\alpha + \varepsilon + \beta(k-k_0), &k\ge k_0
\end{cases}
$$ for $\alpha,\beta, \varepsilon>0$ and $k_0\in\mathbb N$.

@@

$$
\bar F(k) = \begin{cases}
\displaystyle\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0\\
\displaystyle\left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right)\frac{\Gamma(\lambda^*+k_0^\alpha + \varepsilon)/\beta)}{\Gamma\left((k_0^\alpha + \varepsilon)/\beta\right)} \frac{\Gamma\left(k-k_0 + 1 +\frac{k_0^\alpha + \varepsilon}{\beta}\right)}{\Gamma\left(k-k_0 + 1 +\frac{\lambda^* +k_0^\alpha + \varepsilon}{\beta}\right)},&k\ge k_0,
\end{cases}
$${#eq-polysurv}

with $\lambda^*$ satisfying

$$
\hat\rho(\lambda^{*}) = \sum_{n=0}^{k_0}\prod_{i=0}^{n-1}\frac{i^\alpha + \varepsilon}{\lambda^{*}+i^\alpha + \varepsilon} + \left(\frac{k_0^\alpha + \varepsilon}{\lambda^{*}-\beta}\right)\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^{*} + i^\alpha + \varepsilon} = 1,
$$

which has to be solved numerically for most parameter choices. Note that $\lambda>\beta$ since when $\lambda\le \beta$ the infinite sum no longer converges and instead goes to infinity.

@@

$$
\bar F(k) 
%\begin{cases}
%=\displaystyle\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0,\\
\displaystyle\approx \left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right) \left(\frac{\beta(k+1-k_0)}{k_0^{\alpha}+\varepsilon} + 1\right)^{-\lambda^*/\beta},%&k\ge k_0,
%\end{cases}
$$ which is the survival function of the $\text{IGPD}\left(\frac{\beta}{\lambda^*}, \frac{k_0^\alpha + \varepsilon}{\lambda^*},k_0-1\right)$ distribution. This means that, above the threshold of the piecewise preference function, the limiting degree distribution can be approximated by the IGPD with shape parameter $\beta/\lambda^{*}$.

@@

Some examples of the possible degree distributions are shown in the central row of @fig-polylinsurv.

@@

The procedure for recovering the parameters begins with simulating a network from the model with $N=100,000$ vertices and $m=1$ given some set of parameters $\pmb\theta = (\alpha, \beta, \varepsilon, k_0)$, obtaining the degree counts in the form of a vector of degrees $\pmb x = (1,2,\ldots,M)$ and the number of vertices with those degrees $\pmb n$ where $M$ is the maximum degree. However, when it comes to fitting this model to real data in the next section, small degrees are extremely influential and will often cause the model to have a bad fit even though the rest of the data looks similar to that of the simulations; truncating the data above some value, say $l<k_0$, should allow the model to be more effectively fitted. This accounts in some way for the fact that this model only applies to trees, and could not possibly capture the behaviour for nodes with small degrees. Using the p.m.f derived in [@rudas07], the likelihood given that $x_i \ge l$ for all $i =1,2,\ldots,M$ is:

@@

```{r, echo=FALSE, warning=FALSE, cache=FALSE, out.width="80%"}
#| fig-width: 8
#| fig-height: 8
#| fig-cap: Posterior estimates of survival function for data simulated from the proposed model with various combinations of ($\alpha$,$\beta$,$\varepsilon$) and $k_0=20$.
#| label: fig-rec1

>>>>

---
title: Tail Flexibility in the Degrees of Preferential
 Attachment Networks
format:
  nature-pdf:
    fig-pos: 'H'
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-basic
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: natbib
    keep-tex: true
    equal-margins: false
    number-sections: true
author:
  - name: Thomas William Boughen
    affiliations:
      - name: Newcastle University, UK
        id: 1
        department: School of Mathematics, Statistics and Physics
  - name: Clement Lee
    affiliations:
      - ref: 1
  - name: Vianey Palacios Ramirez
    affiliations:
      - ref: 1
abstract: |
  Devising the underlying generating mechanism of a real-life network is difficult as, more often than not, only its snapshots are available, but not its full evolution. One candidate for the generating mechanism is preferential attachment which, in its simplest form, results in a degree distribution that follows the power law. Consequently, the growth of real-life networks that roughly display such power-law behaviour is commonly modelled by preferential attachment. However, the validity of the power law has been challenged by the presence of alternatives with comparable performance, as well as the recent findings that the right tail of the degree distribution is often lighter than implied by the body, whilst still being heavy. In this paper, we study a modified version of the model with a flexible preference function that allows super/sub-linear behaviour whilst also guaranteeing that the limiting degree distribution has a heavy tail. We relate the distributions tail heaviness directly to the model parameters, allowing direct inference of the parameters from the degree distribution alone.
keywords: [networks, discrete extremes, degree distribution]
bibliography: refs.bib

@@

# CL: Overall comments {-}

1. The introduction section is not quite clear and needs a lot of improvement, so here are my suggestions on the outline, in a hopefully more logical flow:
   a. Start with the broad picture e.g. that networks exist in many fields (name some for which you can cite applications), and that statistical methods are have been used to study networks. Some are for revealing the latent / underlying structures of the networks (stochastic block models), some are for explaining some response variables by network properties (ERGMs), and some are for postulating how the network grows and evolves (mechanistic models). Find some references, either the groundbreaking ones or comprehensive reviews to back this up.
   b. Introduce the general PA model as one of the mechanistic models. This will be a natural point to mention the rules (in terms as simple as possible) and introduce the preference function. Mention the special case when $b(k)=k$ and cite @Barabasi99.
   c. Then talk about PA model and mechanistic models in general being useful to **simulate** networks but not be fitted to real data because usually only snapshots are available. This leads well into the point on the degree distribution being informative.
   d. Then in the paragraph starting "When looking at ...", point out that it is the BA model [@Barabasi99] that leads to a power law degree distribution.
   e. Then point out that while it's attempting to attribute to the BA model when degrees seemingly follow the power law, there are two main concerns: first, a general preference function doesn't lead to the power law [@krapivsky01]; second, some claim that a lot of real data don't actually follow the power law. Mention not only @Broido_2019 but also responses to them e.g. @vvvk19.
   f. @vvvk19 leads naturally to the point that extreme value methods have not been used in analysing degree distributions until recently, such as @vvvk19 and @lef24. Not using these methods essentially downweights the deviation of the vertices with large degrees, which have far more influence on the network than those with small degrees, from the power law behaviour.
   g. Also mention Resnick's works (and others) on the crossroads of networks and extremes. Summarise what these papers do.
   h. Come back to the focus on the degree distribution, and point out that most methods, whether extremes are incorporated or not, are descriptive in the sense that no information about the preference function $b(\cdot)$ is revealed, even if PA model was indeed the underlying mechanism.
   i. Then mention that this paper addresses that gap. Specifically, **given the degree distribution of the network assumed to come from the PA model, can we directly infer the model parameters?** While @rudas07 have derived the limiting degree distribution in terms of $b(\cdot)$ and its parameters, we build upon it by finding the class of preference functions that result in realistic tails (heavy but not as heavy as implied by the power law).
   j. Then go straight to the division of the rest of the paper, and conclude the introduction section. The remaining materials should mostly go to the next section, but you can retain some materials if you think they complement (or already address) the above points.
2. Rough outline of Section 2, which should be on the PA model and deriving the tail heaviness of the limiting degree distribution in terms of $b(\cdot)$:
   a. Start with the general description of the PA model. You can move here the paragraphs in the introduction section, starting with "The network generative model ...", "Starting at time ...", and "Special cases of this model ...". Most of what you have written up till the pmf can be kept.
   b. Next, first state that of interest is the tail heaviness (which here refers to the shape parameter of the (integer) GPD approximation of the tail). Then move here the paragraphs on @shimura12 from the introduction.
   c. Then state proposition 2.1 and point to the Appendix for the proof.
   d. Next, we need a bit more discussion and explanation before stating that $b(\cdot)$ has to be asymptotically linear for a heavy tail. First point out that this result covers and aligns with the previously obtained result i.e. @krapivsky01. This is pretty much the paragraph currently under Section 2.1, but with a better flow. You might even include the special case of the special case i.e. $b(k)=k+\epsilon$, to briefly illustrate how a tail heaviness of $0.5$ is obtained for the BA model.
   e. Now, argue that $b(\cdot)$ has to be (asymptotically) linear above a threshold, in order to have a positive tail heaviness, then introduce the proposed preference function as our model, with tail heaviness $\beta/\lambda^{*}$.
   f. Conclude the section by saying that we will examine its property in the next Section (see next point).
3. The section could be called "Preferential attachment with flexible heavy tail", essentially making the subsection a section itself.
   a. Most of the materials can be kept, and the form of the IGPD should be inserted when approximating the survival using Stirling's (not Sterling's) approximation. The survival of the IGPD was in the introduction but I suggest moving it here.
   b. The piecewise linear model doesn't add much, so I would consider excluding it unless there's a point e.g. computational simplicity?
   c. I would conclude the section by moving the likelihood expression here, and say that the parameters can be inferred in a standard way, via the frequentist or Bayesian approach, as the likelihood is an explicit function of the parameters.
4. For simplicity, it's easier to use $m=1$ throughout and only mention the general case $m>1$ as future work in the discussion section. Also, it might be worth just calling the general preferential attachment model without the word "general" throughout, as it is unambiguous that it is the model with a flexible / general $b(\cdot)$, while the BA model is the one with $\b(k)=k+\epsilon$.
5. There are inconsistencies and duplications in various places, probably because you edited at one place and didn't update associated instances elsewhere. Do go back and forth when making edits.
6. The presentation can use many incremental improvements:
   a. use $k$ or $n$ for the integer but not both, unless necessary and in a consistent way. There were places where $n$ was used as the subject initially but it changed to $k$.
   b. ensure that the text in plots are legible.
   c. when citing, use the parentheses correctly, as they have been used inappropriately; in Quarto syntax, the square brackets will automatically put the parentheses (similar to citep in LaTeX).
   d. ensure that the maths don't over the linewidth.
   e. introduce the full term with the acronym in parentheses when using it for the first time, e.g. GPA.
   f. some references of equations are not working e.g. eq-surv?
   g. unless necessary, avoid strong adverbs / adjectives.
7. It seems that you version control all the files, which I won't recommend. Only track the files that you manually change, not the generated ones (cache, pdf, and tex unless you manually created one). This will facilitate the reproducibility. I have removed the generated files in my branch.
8. Consider creating subfolders to store the results, data, figures, etc. This will streamline your file structure. I have accordingly edited the R scripts so that if you run them, the rds files will be stored in results/.
9. Accents in names in bib / tex / qmd might not work on some computers. Here's the conversion chart: https://www.bibtex.org/SpecialSymbols/

@@

Whether the power law is adequate for real degree distributions has become a heated debate, with alternatives such as @Broido_2019 seeming to outperform the power law in some cases. Additionally, @lef24 find that for many real degree distributions the body may follow a power law, the right tail does not or at least seems to be lighter than is implied by the body whilst still being heavy. One method for modelling the tail of the degree distributions of real networks is to use a discretised variation of the generalised Pareto distribution (GPD) usually dubbed the Integer GPD (GPD) where $X|X>v \sim \mathrm{IGPD}(\xi,\sigma,v)$ is defined by the survival:

@@

[CL: Is the precise form of the IGPD needed here? The big picture is probably more important (point 3f in overall comments)]

@@

Estimating the preference function used by network generative models like this is of great interest, with the potential to provide a deeper understanding of the relationships between the vertices in the network. Several papers and an R package (`PAfit`) have been dedicated to estimating the preference function that may have been used when a network was growing; one thing all these have in common is requiring access to a networks evolution data, something that is not always readily available or feasible to access. A method for estimating a preference function without this data available would be extremely useful.

@rudas07 introduces theoretical results for this model with a general preference function in the cases that the network being generated is a tree ($m=1$); presenting an opportunity to design a preference function that will capture the behaviours observed in the degree distributions of real networks. Since they provide theoretical results for the limiting degree distribution, a model of this form would be able to be fitted to the degree distributions of real networks where the full evolution is not available, only a snapshot.

The rest of this paper is as follows: @sec-gpa looks at the theoretical limiting behaviour of a GPA model when $m=1$ according to the results from @rudas07, going on to introduce a flexible class of preference functions that can guarantee a heavy tailed degree distribution while still being flexible in the body. @sec-rec shows that the preference function parameters can be fairly well recovered from the degree distributions of networks simulated from the GPA model using various functions of the class introduced in @sec-gpa. Having shown that for simulated data the model parameters are recoverable from the degree distribution alone, @sec-real builds upon this and attempts to fit the model to degree distributions of real networks; modelling not only the degree distribution itself but also the estimates for the parameters of the preference function assuming the networks evolved according to the GPA scheme. @sec-conc discusses the main results, proposes future work and concludes the paper.

# General Preferential Attachment Model {#sec-gpa}

In this section, we introduce a general preferential attachment model, with the focus on the limiting degree distribution as a function of the preference function $b(\cdot)$ where each vertex brings with it $m$ edges. This preference function is subject to the following conditions:

@@

Given these two conditions an expression for the survival of the limiting degree distribution can be found in the case that $m=1$; obtained by considering a branching process that is equivalent to the growth of the network, as in @rudas07. Theorem 1 from @rudas07 states that for the tree $\Upsilon(t)$ at time $t$:

$$
\lim_{t\rightarrow\infty}\frac{1}{|\Upsilon(t)|}\sum_{x\in\Upsilon(t)}\varphi(\Upsilon(t)_{\downarrow x}) = \lambda^* \int_0^\infty e^{-\lambda^* t}\mathbb E\left[\varphi(\Upsilon(t))\right]dt
$$
where $\lambda^*$ satisfies $\hat\rho(\lambda^*)=1$. (CL: $\hat{\rho}$ has not been defined yet.)

@@

$$
\bar F(k) = \frac{\int_0^\infty e^{-\lambda^* t}\mathbb E\left[\mathbb I\left\{\text{deg}(x,\Upsilon(t))>k\right\}\right]dt}{\int_0^\infty e^{-\lambda^* t}dt} = \prod_{i=0}^k\frac{b(i)}{\lambda^* + b(i)}.
$$
Using the fact that $f(k) = \bar F(k-1) - \bar F(k)$ the probability mass function (pmf) is

$$
f(k) = \frac{\lambda^*}{\lambda^* + b(k)}\prod_{i=0}^{k-1}\frac{b(i)}{\lambda^*+b(i)},\qquad k\in\mathbb N,
$$

@@

$$
\lim_{k\rightarrow\infty}\Omega(F,k) = \lim_{k\rightarrow\infty}\frac{b(k+1)-b(k)}{\lambda^*}.
$$
:::

@@

In @krapivsky01, a preference function of the form $k^\alpha +\varepsilon$ has been considered. However, it has been noted that super-linear preferential attachment ($\alpha > 1$) leads to a degenerate limiting degree distribution where at some point one vertex gains the connection (CL: edge?) from every vertex that joins the network, additionally sub-linear preferential attachment ($\alpha <1$) has been shown to lead to a light tailed limiting degree distribution. Consider a preference function of the form:

$$
b(k) = \begin{cases}
k^\alpha + \varepsilon,&k<k_0,\\
k_0^\alpha + \varepsilon + \beta(k-k_0), &k\ge k_0,
\end{cases}
$$ for $\alpha,\beta, \varepsilon>0$ and $k_0\in\mathbb N$.

@@

$$
\bar F(k) = \begin{cases}
\displaystyle\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0,\\
\displaystyle\left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right)\frac{\Gamma(\lambda^*+k_0^\alpha + \varepsilon)/\beta)}{\Gamma\left((k_0^\alpha + \varepsilon)/\beta\right)} \frac{\Gamma\left(k-k_0 + 1 +\frac{k_0^\alpha + \varepsilon}{\beta}\right)}{\Gamma\left(k-k_0 + 1 +\frac{\lambda^* +k_0^\alpha + \varepsilon}{\beta}\right)},&k\ge k_0,
\end{cases}
$${#eq-polysurv}

with $\lambda^*$ satisfying $\hat{\rho}(\lambda^{*})=1$, where

$$
\hat\rho(\lambda) = \sum_{n=0}^{k_0}\prod_{i=0}^{n-1}\frac{i^\alpha + \varepsilon}{\lambda+i^\alpha + \varepsilon} + \left(\frac{k_0^\alpha + \varepsilon}{\lambda-\beta}\right)\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda + i^\alpha + \varepsilon} = 1,
$$

which has to be solved numerically for most parameter choices. Note that $\lambda$ has to be greater than $\beta$ since when $\lambda\le \beta$ the infinite sum diverges. (CL: Where is the infinite sum?)

@@

$$
\bar F(k) 
%\begin{cases}
%=\displaystyle\prod_{i=0}^{k}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon},&k<k_0,\\
\displaystyle\approx \left(\prod_{i=0}^{k_0-1}\frac{i^\alpha + \varepsilon}{\lambda^*+i^\alpha + \varepsilon}\right) \left(\frac{\beta(k+1-k_0)}{k_0^{\alpha}+\varepsilon} + 1\right)^{-\lambda^*/\beta},%&k\ge k_0,
%\end{cases}
$$ which is the survival function of the $\text{IGPD}\displaystyle\left(\frac{\beta}{\lambda^*}, \frac{k_0^\alpha + \varepsilon}{\lambda^*},k_0-1\right)$ distribution. This means that, above the threshold of the piecewise preference function, the limiting degree distribution can be approximated by the IGPD with shape parameter $\beta/\lambda^{*}$.

@@

Some examples of the limiting degree distributions are shown in the central column of @fig-polylinsurv.

@@

The procedure for recovering the parameters begins with simulating a network from the model with $N=100,000$ vertices and $m=1$ given some set of parameters $\pmb\theta = (\alpha, \beta, \varepsilon, k_0)$, obtaining the degree counts in the form of a vector of degrees $\pmb x = (1,2,\ldots,M)$ and the number of vertices with those degrees $\pmb n$ where $M$ is the maximum degree. However, when it comes to fitting this model to real data in the next section, small degrees are extremely influential and will often cause the model to have a bad fit even though the rest of the data looks similar to that of the simulations; truncating the data above some value, say $l<k_0$, should allow the model to be more effectively fitted. This accounts in some way for the fact that this model only applies to trees, and could not possibly capture the behaviour for nodes with small degrees. Using the p.m.f derived in @rudas07, the likelihood given that $x_i \ge l$ for all $i =1,2,\ldots,M$ is:

@@

```{r, echo=FALSE, warning=FALSE, cache=FALSE, out.width="95%"}
#| fig-width: 8
#| fig-height: 8
#| fig-cap: Posterior estimates of survival function for data simulated from the proposed model with various combinations of ($\alpha,\beta,\varepsilon$) and $k_0=20$.
#| label: fig-rec1
